Steve Linberg

### 2022-08-18 steve.Rmd
text updates

I am a Masters student in the [DACSS program](https://www.umass.edu/sbs/data-analytics-and-computational-social-science-program) at the University of Massachusetts, Amherst; anticipated graduation Summer 2022. The day job is Senior Systems and Analytics Engineer at the [Gandara Center](https://www.gandaracenter.org/) in West Springfield, MA.

@@

**Hampshire College** | Amherst, MA

BA, Social Science, 1990-3

**University of Massachusetts, Amherst** | Amherst, MA

M.S, Data Analytics and Computational Social Science | Anticipated graduation summer 2022

@@

**Gandara Center** | Senior Systems and Analytics Engineer / CIO / IT Director | 2005 - Present

**Silicon Goblin Technologies** | Owner / Programmer | 1999 - 2015

**National Center on Adult Literacy**, University of Pennsylvania Graduate School of Education | Systems Programmer | 1997-1999

**Holyoke Public Schools** | Literacy and GED Instructor | 1994-1997

**Unicom, Inc.** | Systems Programmer and Technical Writer | 1983-1997

@@

- Data analytics and statistics
- Programming languages
- The state of the world
- Drawing, painting, guitar, motorcycles, baking, gaming

>>>>

In summer 2022, I completed the [Data Analytics and Computational Social Science (DACSS) Masters program](https://www.umass.edu/sbs/data-analytics-and-computational-social-science-program) at the [University of Massachusetts, Amherst](https://umass.edu). My present position is Senior Systems and Analytics Engineer at the [Gandara Center](https://www.gandaracenter.org/) in West Springfield, MA.

@@

*MS, Data Analytics and Computational Social Science* | 2022

University of Massachusetts, Amherst | Amherst, MA

*BA, Social Science* | 1992

Hampshire College | Amherst, MA

@@

**Gandara Center**, West Springfield, MA | Senior Systems and Analytics Engineer / CIO / IT Director | 2005 - Present

**Silicon Goblin Technologies**, Amherst, MA | Owner / Programmer | 1999 - 2015

**Rojo Networks**, San Francisco, CA | Systems Administrator and Customer Service Lead | 2006-2008

**National Center on Adult Literacy**, University of Pennsylvania Graduate School of Education, Philadelphia, PA | Systems Programmer and Lead Web Developer | 1997-1999

**Holyoke Public Schools**, Holyoke, MA | Literacy and GED Instructor | 1994-1997

**Unicom, Inc.**, Providence, RI | Systems Programmer and Technical Writer | 1983-1997

@@

- Data analytics, statistics, machine learning
- Software engineering
- Politics, culture and the state of the world
- Drawing, painting, guitar, motorcycles, baking, gaming
